Adaptive Preregistration for Modelling

### 2024-03-12 preregistration_modelling.qmd
template typo and formatting updates
Signed-off-by: egouldo <egouldo@users.noreply.github.com>

::: callout-caution
-   [ ] What degree of flexibility is required from the model? Might the model need to be quickly reconfigured to explore new scenarios or problems proposed by clients / managers / model-users?
-   [ ] Are there any limitations on model development analysis and flexibility, such as time or budget constraints, for example, does a model need to be deployed rapidly?
    -   [ ] When must the model be completed by, e.g. to help make a decision?
:::

@@

### Explain how you will operationalise response and predictor variables, and covariates

@@

@@

::: callout-caution
The consequences of assumption violations on the interpretation of results should be assessed [@Araujo2019].

>>>>

-   [ ] What degree of flexibility is required from the model? Might the model need to be quickly reconfigured to explore new scenarios or problems proposed by clients / managers / model-users?
-   [ ] Are there any limitations on model development analysis and flexibility, such as time or budget constraints, for example, does a model need to be deployed rapidly?
    -   [ ] When must the model be completed by, e.g. to help make a decision?
:::

@@

### Operationalising Model Variables

@@

:::

::: callout-caution

@@

The consequences of assumption violations on the interpretation of results should be assessed [@Araujo2019].
